\section{Evaluation and Discussion}

\subsection{Benchmark Design and Evaluation Metrics}

The system is evaluated on a fixed benchmark of 100 questions. The benchmark is designed to test the assistant as a complete legal question-answering system, not only as a text generator. It includes 94 in-corpus questions and 6 out-of-corpus questions. For in-corpus questions, the expected behavior is to retrieve the required legal basis and produce a grounded answer. For out-of-corpus questions, the expected behavior is to refuse the question or mark the answer as insufficient-context.

The benchmark covers different types of Vietnamese labor-law questions, including direct questions, definitions, document guidance, exceptions, multi-hop questions, table and appendix lookup, hard-negative citation cases, paraphrased user questions, dispute procedures, comparisons, scenarios, and unsupported topics.

The evaluation uses deterministic checks instead of subjective scoring alone, while following the broader goal of RAG evaluation: measuring retrieval quality, answer faithfulness, and grounding. This is important because a fluent legal answer may still be wrong if it cites the wrong article, misses a required legal basis, or answers a question outside the indexed corpus. Therefore, the evaluation focuses on retrieval quality, citation grounding, answer quality, and refusal behavior.

The benchmark design is also related to legal NLP evaluation efforts, which emphasize domain-specific reasoning and legal text understanding rather than general text fluency alone.

Table~\ref{tab:evaluation-metrics-draft} summarizes the main evaluation metrics used in this thesis.

\begin{table}[H]
  \centering
  \caption{Evaluation Metrics Summary}
  \label{tab:evaluation-metrics-draft}
  \small
  \begin{tabularx}{\linewidth}{@{}L{0.25\linewidth}L{0.34\linewidth}Y@{}}
    \toprule
    Metric & What it measures & Main interpretation \\
    \midrule
    Recall@10 & Whether required legal citations appear in the top retrieved contexts. & Higher values indicate better recovery of required evidence. \\
    Required citation coverage & Whether the retriever finds the expected legal bases for in-corpus questions. & Measures evidence completeness before answer generation. \\
    Forbidden citation violation rate & Whether distracting or invalid citations appear in retrieved results. & Lower values indicate cleaner retrieval and graph expansion. \\
    Retrieval pass rate & Whether retrieval satisfies required and forbidden citation checks. & Shows whether the answer layer receives usable legal evidence. \\
    Answer pass rate & Whether the generated answer satisfies deterministic answer-quality checks. & Measures answer adequacy after evidence selection. \\
    Citation validation pass rate & Whether cited legal bases are supported by retrieved contexts. & Measures citation containment and grounding. \\
    Adjusted end-to-end pass rate & Whether the full pipeline passes retrieval, answer, citation, and refusal checks. & Summarizes complete system behavior. \\
    Out-of-corpus QA pass rate & Whether unsupported questions are refused or marked insufficient-context. & Measures conservative scope behavior. \\
    \bottomrule
  \end{tabularx}
\end{table}

Table~\ref{tab:benchmark-composition-draft} shows the composition of the 100-question benchmark.

\begin{table}[H]
  \centering
  \caption{Benchmark Composition}
  \label{tab:benchmark-composition-draft}
  \begin{tabular}{@{}lr@{}}
    \toprule
    Category & Queries \\
    \midrule
    Direct QA & 19 \\
    Definition QA & 7 \\
    Document guidance QA & 10 \\
    Exception-based QA & 11 \\
    Multi-hop QA & 7 \\
    Table and appendix lookup & 10 \\
    Hard-negative citation QA & 5 \\
    Paraphrased real-user QA & 5 \\
    Labor dispute and procedure QA & 5 \\
    Procedure QA & 7 \\
    Comparison QA & 4 \\
    Scenario-based QA & 4 \\
    Out-of-corpus QA & 6 \\
    \midrule
    Total & 100 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Retrieval Results}

The first evaluation step measures whether the system can retrieve the required legal evidence. This is important because the final answer depends on the quality of retrieved contexts. If the correct legal provisions are not retrieved, the answer generation step may not have enough evidence to produce a valid response.

Two retrieval settings are compared. The first setting uses hybrid retrieval only. In this setting, the system retrieves evidence from Qdrant using dense and sparse search signals. The second setting enables graph-augmented retrieval. In this setting, the system starts from Qdrant results and then expands related evidence through the Neo4j legal graph.

Table~\ref{tab:retrieval-results-draft} reports the retrieval results.

\begin{table}[H]
  \centering
  \caption{Retrieval and Graph Expansion Results}
  \label{tab:retrieval-results-draft}
  \begin{tabular}{@{}lrrrrr@{}}
    \toprule
    Mode & Queries & Recall@10 & Coverage & Forbidden rate & Pass rate \\
    \midrule
    Hybrid-only & 94 & 0.735 & 0.735 & \cG{0.032} & 0.649 \\
    Graph-augmented & 94 & \cB{0.835} & \cB{0.835} & \cR{0.043} & \cB{0.766} \\
    \bottomrule
  \end{tabular}
\end{table}

The results show that graph-augmented retrieval improves Recall@10 from 0.735 to 0.835. The retrieval pass rate also increases from 0.649 to 0.766. This means that the legal graph helps the system recover relevant provisions that hybrid retrieval alone may miss.

However, graph expansion also slightly increases the forbidden citation violation rate, from 0.032 to 0.043. This shows an important trade-off. Legal graph connections can help recover missing evidence, but they can also introduce related provisions that are not valid for the specific question. Therefore, graph expansion must be controlled carefully and should not simply add every connected legal node.

\subsection{End-to-End Results}

The second evaluation step measures the full question-answering pipeline. This includes retrieval, context assembly, answer generation, citation validation, and refusal behavior.

Table~\ref{tab:e2e-results-draft} reports the final end-to-end results.

\begin{table}[H]
  \centering
  \caption{End-to-End QA and Citation Validation Results}
  \label{tab:e2e-results-draft}
  \begin{tabular}{@{}lr@{}}
    \toprule
    Metric & Value \\
    \midrule
    Total benchmark queries & 100 \\
    Adjusted end-to-end pass rate & 0.780 \\
    Retrieval pass rate & 0.780 \\
    Answer pass rate & \cG{0.980} \\
    Citation validation pass rate & \cB{1.000} \\
    Quality validation pass rate & \cG{0.980} \\
    Average final quality score & 94.11 \\
    Low-information quotes & 1 \\
    Unsupported article numbers & \cB{0} \\
    Unretrieved citations & \cB{0} \\
    Out-of-corpus QA pass rate & \cB{1.000} \\
    Graph expansion used & 89 queries \\
    Average graph depth & 2.160 \\
    \bottomrule
  \end{tabular}
\end{table}

The final adjusted end-to-end pass rate is 0.780. The answer pass rate is 0.980, while the citation validation pass rate is 1.000. The out-of-corpus QA pass rate is also 1.000. These results show that the system is strong at keeping generated citations inside retrieved evidence and refusing unsupported questions.

The main limitation is retrieval. The retrieval pass rate is also 0.780, which indicates that most end-to-end failures come from missing or incomplete retrieved evidence rather than from citation hallucination after generation. In other words, once the system has the correct legal context, the answer and citation validation components usually behave reliably.

\subsection{Category-Level Results}

The benchmark results are not uniform across all question types. The system performs well on direct questions, definition questions, document guidance questions, exception-based questions, comparison questions, procedure questions, and scenario-based questions. These categories usually require legal evidence that can be retrieved directly or with limited expansion.

The weaker categories are labor-dispute procedure questions, hard-negative citation questions, paraphrased real-user questions, multi-hop questions, and table or appendix lookup. These failures are expected because these categories require more complex evidence selection. For example, table lookup may require retrieving a specific appendix or table row. A paraphrased question may hide the legal concept behind informal wording. A hard-negative case may contain provisions that are legally related but not actually valid for the answer.

This pattern shows that graph expansion improves retrieval, but it does not solve every retrieval problem. The system still needs stronger query understanding, better table-aware retrieval, and more precise filtering of legally related but distracting provisions.

\subsection{Case Studies and Error Taxonomy}

To better understand the system behavior, representative successful and failed cases are analyzed. Successful cases show that the system can answer correctly when the required legal basis is retrieved. For example, retirement-age questions can combine the Labor Code with Decree 135/2020/ND-CP table evidence. Out-of-corpus questions, such as minimum wage by region, are refused because the relevant legal instrument is not included in the indexed corpus.

Failed cases show where the current system remains limited. Some paraphrased questions fail because the system does not map the user's wording to the correct legal concept. Some table or appendix questions fail because the required evidence is stored in a more structured form than ordinary text. Some hard-negative cases fail because the graph adds legally related provisions that are close to the topic but not correct for the specific answer.

Table~\ref{tab:error-taxonomy-draft} summarizes representative cases and error types.

\begin{table}[H]
  \centering
  \caption{Case Studies and Error Taxonomy}
  \label{tab:error-taxonomy-draft}
  \small
  \begin{tabularx}{\linewidth}{@{}L{0.28\linewidth}L{0.22\linewidth}Y@{}}
    \toprule
    Case or error & Result & Interpretation \\
    \midrule
    Female retirement age in 2026 & \cB{Pass} & Retrieved Labor Code and Decree 135 table evidence. \\
    Minimum wage by region in 2026 & \cB{Pass refusal} & Correctly identified insufficient indexed context. \\
    Temporary transfer paraphrase & \cR{Fail} & Missed Labor Code Article 29 required citations. \\
    Domestic worker contract template & \cR{Fail} & Missed appendix/form evidence and produced low-information answer. \\
    Holiday overtime pay hard negative & \cR{Fail} & Mixed missing citation with over-expansion to overtime limit provisions. \\
    Labor-dispute court choice & \cR{Fail} & Cross-code procedure retrieval remained incomplete. \\
    \midrule
    Retrieval missing required context & 20 cases & Dominant failure reason. \\
    Retrieval over-expansion & 4 cases & Related but forbidden citations entered top results. \\
    Low-information answer & 2 cases & Extractive answer lacked enough useful rule content. \\
    Answer missing required rule & 1 case & Answer quality failed after retrieval gap. \\
    \bottomrule
  \end{tabularx}
\end{table}

The dominant failure reason is missing required context. This confirms that the main bottleneck is still retrieval and evidence selection. Citation validation is reliable in the final run, but it cannot recover a legal basis that was not retrieved in the first place.

\subsection{Discussion}

The evaluation supports the main design choice of this thesis. Legal question answering benefits from combining text retrieval with legal structure. Hybrid retrieval is useful for finding semantically and lexically relevant provisions, while graph expansion helps recover related legal evidence through hierarchy, cross-references, and implementation relationships.

The improvement from 0.735 to 0.835 in Recall@10 shows that Neo4j contributes useful evidence beyond flat retrieval. This is especially important in Vietnamese labor law, where a complete answer may depend on several connected documents. A Labor Code provision may need a decree for implementation details, or a circular or appendix may provide the practical information needed by the user.

At the same time, the results show that graph expansion must be controlled. The increase in forbidden citation violations means that legal relatedness is not always the same as answer relevance. A neighboring provision in the graph may be connected to the topic, but still not be the correct legal basis for the question. This is why the system uses policy-controlled expansion, filtering, reranking, and context budgeting.

The strongest result of the system is citation containment. The final citation validation pass rate is 1.000, with no unretrieved citations and no unsupported article numbers in the final run. This does not prove that every legal interpretation is perfect, but it shows that the system can keep its citations within retrieved evidence. For a scoped legal information assistant, this is an important safety property.

The main remaining weakness is retrieval robustness. Informal user questions, table-heavy answers, hard-negative cases, and cross-document procedure questions still create errors. Future improvement should therefore focus less on making the language model more fluent and more on improving query rewriting, table retrieval, graph filtering, and legal evidence selection.

\subsection{Threats to Validity}

The evaluation has several limitations. First, the benchmark is manually constructed and contains 100 questions. Although it covers several important question types, it cannot represent all possible Vietnamese labor-law questions.

Second, the system is evaluated within a scoped corpus of selected legal documents. The results should not be interpreted as coverage of all Vietnamese law. Questions that require documents outside this corpus may still be unsupported.

Third, deterministic validation is useful for reproducibility, but it cannot fully replace expert legal review. It can check whether citations are retrieved and whether some answer rules are satisfied, but it cannot judge every possible issue of legal interpretation.

Fourth, the final reproducible evaluation uses deterministic extractive generation. This makes the results stable, but it may produce answers that are less fluent than the deployed language-model path. Therefore, the evaluation should be understood as a test of the citation-grounded pipeline rather than a complete measurement of user-facing answer quality.

Finally, the results depend on the fixed benchmark, index manifest, and evaluation outputs used in this thesis. Future work should extend the benchmark with more real user questions, expert-reviewed answers, temporal validity checks, and a larger versioned legal corpus.
