\chapter{List of Legal Documents}
\todotext{List the six legal documents used in the final corpus, including official titles, document IDs, effective dates, source URLs, document type, normative rank, and chunk counts.}

\begin{table}[H]
  \centering
  \caption{Appendix document list placeholder.}
  \label{tab:appendix-document-list}
  \footnotesize
  \begin{tabular}{p{0.26\linewidth}p{0.22\linewidth}p{0.18\linewidth}p{0.22\linewidth}}
    \toprule
    Document ID & Official Title & Source URL & Notes \\
    \midrule
    45-2019-qh14 & TODO & TODO & Labor Code 2019 \\
    92-2015-qh13-labor-only & TODO & TODO & Labor-related procedure provisions \\
    nghi-dinh-135-2020-nd-cp & TODO & TODO & Retirement age guidance \\
    nghi-dinh-145-2020-nd-cp & TODO & TODO & Labor Code implementation \\
    thong-tu-09-2020-tt-bldtbxh & TODO & TODO & Circular guidance \\
    thong-tu-10-2020-tt-bldtbxh & TODO & TODO & Circular guidance \\
    \bottomrule
  \end{tabular}
\end{table}

\chapter{Chunk Schema}
\todotext{Document the JSONL schema for legal chunks and enriched chunks, including required fields, optional fields, and validation rules.}

\chapter{Graph Schema}
\todotext{Document Neo4j labels, relationship types, properties, constraints, indexes, and example Cypher queries.}

\chapter{Benchmark Samples}
\todotext{Add representative benchmark samples with question text, category, difficulty, required citations, forbidden citations, graph-required label, and normative-hierarchy-required label. Do not include fabricated examples.}

\chapter{Evaluation Metrics}
\todotext{Define retrieval metrics, answer validation checks, citation validation checks, and pass/fail aggregation. Include formulas used by the evaluation scripts.}

\chapter{Reproducibility Commands}
\todotext{Copy final reproducibility commands from \texttt{artifacts/evaluation/reproducibility\_notes.md}, including retrieval-mode evaluation, end-to-end evaluation, optional vector index rebuild, and optional Neo4j graph rebuild.}

\chapter{Example Retrieved Contexts and Answers}
\todotext{Insert selected retrieved contexts and generated answers for the Chapter 5 case studies after choosing final examples from the evaluation outputs.}
