\chapter{Introduction}

\section{Background}
Information retrieval and question answering (QA) systems have become essential tools across many professional domains, including the legal sector. However, legal question answering differs fundamentally from general open-domain QA. In a legal context, an answer is only valid if it is grounded in the correct statutory text and accompanied by precise legal citations. Users—whether employees, employers, or legal advisors—require answers that preserve the specific hierarchical context of documents, articles, clauses, and points rather than simple semantic matches. Without accurate citations, an answer lacks legal authority and cannot be verified, which limits its practical utility for compliance or dispute resolution.

This research was originally motivated by a specific, high-frequency legal challenge: employment contract termination. Initially framed as ``A Case Study on Employment Contract Termination,'' the project aimed to build an information assistant to guide users through the complex rules surrounding how labor relations end. Under Vietnamese law, termination disputes are highly sensitive, and incorrect administrative steps can lead to legal risk, financial consequences, or disputes. Providing accurate, citation-grounded answers for these scenarios is critical for both business compliance and employee advocacy.

However, during initial system design and testing, it became evident that contract termination cannot be treated as an isolated legal topic. A single inquiry about terminating an employment contract frequently depends on a wide range of broader labor-law provisions. For example, verifying whether a termination is lawful requires checking the underlying labor contract rules (such as contract types, probation periods, and mandatory contents) and the fundamental rights and obligations of both employees and employers. Determining the financial outcomes of termination requires traversing complex severance and compensation rules. Furthermore, special protection regimes, such as minor worker rules, and retirement age provisions, introduce distinct exceptions and tables that alter termination conditions. Finally, resolving these issues often involves analyzing labor dispute resolution and civil procedure provisions to determine court jurisdictions and mediation timelines.

Because of these interconnected legal dependencies, the scope of this project was expanded beyond a narrow, topic-specific case study. To provide a reliable and broader scoped labor-law QA system, the system must cover the broader, structured network of Vietnamese labor law. This expanded corpus is composed of six key legislative and administrative documents: the Labor Code 2019, a labor-related subset of the Civil Procedure Code 2015, Decree 135/2020/NĐ-CP (governing retirement ages), Decree 145/2020/NĐ-CP (governing general labor conditions), Circular 09/2020/TT-BLĐTBXH (governing minor workers), and Circular 10/2020/TT-BLĐTBXH (governing contract templates).

Traditional information retrieval methods and standard Retrieval-Augmented Generation (RAG) pipelines \cite{lewis2020retrieval} struggle with this hierarchical and cross-referenced complexity. Standard RAG architectures split documents into flat, fixed-size text windows that ignore the nested legal grammar. This arbitrary chunking frequently separates critical points from their parent articles or documents, causing semantic fragmentation. Moreover, standard RAG models operate primarily on semantic text similarity, meaning they can easily miss cross-referenced provisions, implementing decrees, circulars, and appendices that reside in different parts of the corpus.

Graph-augmented retrieval (or GraphRAG) provides a promising path forward by representing legal corpora as structural knowledge graphs. In this approach, nodes represent legal documents, articles, clauses, points, and appendices, while edges model the deterministic hierarchies, cross-references, taxonomic associations, and normative authority relations between them. By using vector-based semantic search to find initial ``seed'' chunks and then performing topological graph expansions, the system can dynamically retrieve related circulars, implementing decrees, and procedural rules. This integration of hybrid vector search and structured graph traversals helps ensure that the downstream generator receives all necessary legal context, improving the completeness and citation accuracy of the generated answers.

\section{Problem Statement}
Standard Retrieval-Augmented Generation systems typically rely on flat retrieval strategies. In these architectures, documents are processed into flat, sequential text blocks and stored in a vector database as isolated records. When a user asks a question, the retriever fetches a set of candidate chunks based solely on semantic vector similarity. While this approach works well for general knowledge-retrieval tasks, it introduces severe limitations in the legal domain, where statutory context is highly integrated.

Within the context of this project, a narrow termination-only dataset would be insufficient to support reliable question answering. Because legal rules are highly interdependent, many contract termination questions depend on broader legal provisions that lie outside the immediate topic of dismissal. For example, a user asking about a termination notice period might actually require a lookup in retirement age tables or contract-type definitions, and a question about wrongful dismissal remedies requires civil procedural rules to determine court jurisdiction. \textbf{The initial case study revealed the need for a broader scoped labor-law corpus.} Treating nested legal provisions as isolated, flat chunks can lead to incomplete answers. Under standard vector search, a ministerial circular that details a Labor Code article may not exhibit enough keyword or semantic overlap to be retrieved alongside its parent code, leaving the system with an incomplete representation of the relevant law.

Furthermore, relying on generative language models to write legal answers introduces the risk of citation hallucinations. If the inline citations generated in the final response are not rigorously validated, the model may cite unsupported provisions or reference incorrect article numbers, which is unacceptable in regulatory compliance.

Therefore, this project investigates how to combine vector retrieval, structured legal graph expansion, and deterministic validation to improve citation-grounded Vietnamese labor-law question answering. To address these challenges, we need a system that integrates hierarchy-aware legal chunking to preserve statutory structures, hybrid vector-sparse retrieval to capture exact coordinates, graph expansion to navigate cross-references, and deterministic citation validation to verify that the cited legal basis and article coordinates are supported by the retrieved context. We aim to investigate these techniques within the indexed corpus and the constructed benchmark, without claiming universal correctness or suggesting that the software can replace human legal experts.

\section{Research Objectives}
To address the limitations of flat retrieval and citation hallucinations in legal QA, this research aims to design, implement, and evaluate a graph-augmented RAG pipeline for Vietnamese labor law. The primary objective is to investigate how combining hybrid vector search with topological graph expansion and rule-based validation affects the retrieval recall and citation grounding of generated answers within a scoped corpus.

Specifically, the project pursues the following concrete research objectives:
\begin{enumerate}
    \item \textbf{Corpus Construction}: Build a scoped Vietnamese labor-law corpus consisting of six key legal and administrative documents, spanning different normative ranks, to support broad labor-law inquiries.
    \item \textbf{Hierarchy-Aware Chunking}: Implement a syntax-aware chunking pipeline that parses legal texts at logical leaf-level boundaries (clauses or points) rather than arbitrary character lengths, preserving the document-to-article-to-clause-to-point structure.
    \item \textbf{Metadata Enrichment}: Develop a rule-based enrichment layer to attach domain-specific metadata—including legal topics, targeted actors, issue types, document types, canonical citation texts, and legislative normative ranks—to each chunk.
    \item \textbf{Hybrid Indexing}: Build a vector and hybrid retrieval index in a Qdrant database, utilizing dense SBERT embeddings and sparse lexical tokens to match semantic concepts and exact article coordinates concurrently.
    \item \textbf{Knowledge Graph Design}: Construct a Neo4j legal knowledge graph that represents the structural hierarchies, resolved cross-references, rule-based taxonomic associations, and normative authority relationships within the corpus.
    \item \textbf{Graph-Augmented Retrieval}: Implement a runtime retrieval expansion policy that uses Qdrant hybrid search hits as entry points (seed nodes) and traverses the Neo4j relational graph to gather parent contexts, implementing regulations, and coordinate fallbacks.
    \item \textbf{Grounded Generation and Validation}: Establish an answering pipeline that generates citation-grounded responses and applies deterministic, rule-based validation checks to verify that the cited legal basis and article coordinates are supported by the retrieved context.
    \item \textbf{System Evaluation}: Design a diagnostic evaluation setup and measure the retrieval recall, Required Citation Coverage, Forbidden Citation Violation Rate, and end-to-end pipeline pass rates over a constructed 69-query benchmark.
\end{enumerate}

\section{Scope of the Project}
Defining the boundaries of this research is critical to establish the validity and limits of our findings. The project began as a case study on employment contract termination, focusing on the specific rules and disputes surrounding how labor relations end. However, because resolving contract termination inquiries requires broad statutory context, the final implementation was expanded to cover a broader Vietnamese labor-law question answering system. \textbf{The final scope should therefore be understood as a scoped Vietnamese labor-law QA system, expanded from the initial employment-contract-termination case study.}

The proposed system is strictly limited to the six indexed Vietnamese labor-law and labor-procedure documents in our corpus. These documents comprise: the Labor Code 2019, a labor-related subset of the Civil Procedure Code 2015, Decree 135/2020/NĐ-CP, Decree 145/2020/NĐ-CP, Circular 09/2020/TT-BLĐTBXH, and Circular 10/2020/TT-BLĐTBXH. The system's knowledge and retrieval capabilities do not extend to other Vietnamese legislation, administrative guidelines, or regulatory domains.

The system is designed strictly for legal information assistance and compliance guidance within the boundaries of this indexed corpus. It acts as an automated tool to help users navigate and locate relevant statutory passages, coordinate tables, and procedural rules. Under no circumstances should the system's output be construed as professional, certified legal advice. Legal inquiries often involve highly subjective scenarios, changing regional practices, or unwritten judicial precedents that cannot be captured by an automated information retrieval system.

Furthermore, the evaluation of the system is conducted using a software-level, deterministic, rule-based validation framework over a controlled benchmark of 69 diagnostic queries. This project does not employ human legal expert reviews as the final evaluation method to verify the legal correctness of the system's reasoning in a live environment. Similarly, we do not rely on LLM-as-Judge metrics as the final measure of answer quality, recognizing that neural evaluators introduce stochastic volatility and their own potential biases. Instead, all performance metrics—including retrieval recall, Required Citation Coverage, and end-to-end pass rates—are computed programmatically against our constructed benchmark annotations within the scoped corpus. While this deterministic approach ensures high reproducibility and transparent system verification, it remains a software-level evaluation and does not guarantee that the generated answers would be accepted as legally binding by a court of law or practicing attorneys.

\section{Contributions}
This thesis contributes a modular, reproducible software framework for citation-grounded question answering in the Vietnamese legal domain. The key contributions of this research are:
\begin{enumerate}
    \item \textbf{Structured Vietnamese Labor Law Corpus}: A cleaned, normalized, and structured digital corpus consisting of six core labor-law and labor-procedure documents, which provides a high-relevance domain for evaluating legal information retrieval.
    \item \textbf{Hierarchy-Aware Legal Chunking Pipeline}: A parser that programmatically identifies chapter, article, clause, and point boundaries in Vietnamese statutory texts, producing chunks that align with the physical document structure.
    \item \textbf{Rule-Based Metadata Enrichment}: A deterministic metadata enrichment pipeline that maps legal topics, targeted actors, issue types, and normative ranks to each chunk, along with formal canonical citation strings.
    \item \textbf{Hybrid Indexing and Retrieval Setup}: An indexing configuration in the Qdrant vector database that fuses dense Sentence-BERT embeddings with sparse lexical tokens and coordinate metadata, enabling concurrent semantic and exact-coordinate prefetching.
    \item \textbf{Deterministic Legal Knowledge Graph}: A Neo4j legal graph schema that models structural hierarchies, cross-document reference links (representing details and guided-by relationships), rule-based taxonomy tags, and normative validity rankings.
    \item \textbf{Graph-Augmented Retrieval Engine}: A runtime query expansion policy that uses hybrid retrieval hits as entry points and traverses the knowledge graph to gather parent articles, implementing regulations, and related procedural guidelines.
    \item \textbf{Citation-Grounded Answer Generation with Validation}: An extractive and generative answering pipeline that synthesizes responses and runs them through a deterministic validation layer to enforce citation and coordinate grounding.
    \item \textbf{Diagnostic Benchmark and Evaluation Framework}: A constructed benchmark of 69 diagnostic queries categorized by difficulty and functional types, along with a reproducible script-based evaluation framework to measure information retrieval and end-to-end pipeline pass rates.
\end{enumerate}

\section{Thesis Structure}
The remainder of this thesis is organized into six chapters, structured as follows:
\begin{itemize}
    \item \textbf{Chapter 2: Background and Related Work} provides a review of the theoretical foundations of Large Language Models (LLMs), Retrieval-Augmented Generation (RAG) architectures, and the challenges of domain-specific legal question answering. It also surveys the use of knowledge graphs in information retrieval, graph-augmented RAG techniques, and contemporary evaluation methodologies.
    \item \textbf{Chapter 3: System Design and Methodology} outlines the conceptual architecture of the proposed system. It details the offline ingestion pipeline, including hierarchy-aware chunking and metadata enrichment, the design schema of the Neo4j legal knowledge graph, the hybrid retrieval formulation, and the online query routing and graph expansion policies.
    \item \textbf{Chapter 4: Implementation} describes the concrete technology stack, software components, and databases used to construct the system. It covers the Python-based data engineering scripts, the Docker containerization of Neo4j, the Qdrant indexing configuration, the Cypher-based graph traversal algorithms, the answer validation gates, and the reproducibility of the evaluation environment.
    \item \textbf{Chapter 5: Evaluation and Results} presents the empirical results of our experiments. It describes the design of the constructed 69-query benchmark, the retrieval evaluation metrics (Recall, Required Citation Coverage, and Forbidden Citation Violation Rate), the end-to-end pipeline pass rates, and provides detailed qualitative case studies of representative legal queries.
    \item \textbf{Chapter 6: Discussion} analyzes the experimental findings in detail. It evaluates the impact of the hybrid vector-sparse retrieval layer, the effectiveness of the graph expansion policies, the strengths of deterministic validation, and identifies key failure modes, structural limitations, and practical deployment considerations.
    \item \textbf{Chapter 7: Conclusion and Future Work} summarizes the main findings of this research, details the academic contributions, and outlines promising future research directions, such as extending the corpus to broader administrative statutes and developing expert-validated evaluation datasets.
\end{itemize}
