\chapter{Discussion}
\label{ch:discussion}

\section{Key Findings}
The empirical results compiled across the experimental evaluations demonstrate the effectiveness of combining structured data processing, hybrid indexing, and relational graph expansion. On the constructed 69-query benchmark and within the indexed six-document corpus, the proposed system achieved complete retrieval coverage and a 1.000 end-to-end pass rate under strict, deterministic validation gates. The primary findings indicate that hierarchy-aware chunking produces highly clean and structurally intact evidence units that preserve legal meaning. Furthermore, graph-augmented retrieval successfully addresses the limits of semantic and keyword search by traversing administrative ties, significantly improving required citation coverage. Finally, the automated validation layer provides a reliable, reproducible, and transparent mechanism to check answer grounding and citation validity, verifying that every legal assertion is backed by retrieved source evidence.

\section{Impact of Hierarchical Chunking}
Granular evidence localization is a major factor in legal information retrieval, where arbitrary character-limit or token-limit sliding windows frequently fragment statutory provisions. Hierarchical chunking by Article, Clause, and Point preserves the structural unity of legal texts, ensuring that provisions are never bisected or separated from their primary contextual anchors. By maintaining parent-child relations (such as linking a specific Point to its parent Clause and parent Article), the data processing pipeline ensures that the retriever retains crucial environmental details and legislative context. Consequently, when a specific clause is retrieved, the system can preserve and format the full citation path, enabling precise downstream citation validation and preventing the loss of adjacent qualifying terms or exceptions.

\section{Benefits of Graph-Augmented Retrieval}
The comparative analysis of retrieval modes in Chapter 5 highlights the advantages of traversing relational legal networks. While hybrid retrieval achieves a strong Recall@10 of 0.920 on the 69-query benchmark, the graph-augmented retriever reaches a Recall@10 of 1.000 and 1.000 required citation coverage. Rather than relying solely on semantic proximity or keyword matching, which struggle when legal concepts are expressed through disparate lexical terms, the graph retriever utilizes hybrid search hits as seed nodes and traverses structural, taxonomy, and reference edges. This relational expansion is especially beneficial for document guidance queries, multi-hop questions, administrative table lookups, and questions requiring the coordination of parent Code acts with implementing Decrees and ministerial Circulars. However, these improvements are benchmark-specific and do not suggest that graph traversal always improves every possible legal query, particularly where user questions map directly to isolated, self-contained statutory articles.

\section{Role of Normative Hierarchy in Legal QA}
Vietnamese legislation is organized in a strict, vertical normative hierarchy where primary laws (such as the Labor Code) establish broad regulatory regimes, while executive Decrees and ministerial Circulars define administrative details, exceptions, and procedural guidelines (i.e., Code/Law $>$ Decree $>$ Circular). The graph model incorporates these normative ranks as discrete properties and directed \texttt{GUIDED\_BY} edges, enabling the system to order retrieved context chunks based on their legislative authority. By enforcing authority constraints, the retriever prioritizes primary statutes over lower-level administrative guidance when both are available in the retrieved window. This hierarchical structuring prevents the generator from relying exclusively on lower-level circulars while neglecting parent code provisions, thereby aligning the system's context assembly with standard legal interpretation principles.

\section{Citation Grounding and Hallucination Control}
Hallucination represents a major safety concern when deploying large language models in regulatory and statutory environments, where fabricated citations or phantom article numbers can lead to serious compliance violations. The implemented architecture addresses this challenge by running the generated response payload through a closed-loop, rule-based validation gate. This gate performs set-theoretic checks to verify that every citation and numerical coordinate present in the answer is present within the actively retrieved context blocks. By restricting the generator's legal basis references to verified source chunks and deploying an extractive fallback when LLM validation checks fail, the system significantly reduces unsupported legal references and coordinate drift. However, while these deterministic validation rules effectively detect and block ungrounded assertions on the benchmark queries, they do not completely eliminate the risk of hallucination under all potential generation conditions.

\section{Practical Applications}
The modular, validated nature of the proposed system makes it well-suited for several practical information retrieval use cases. It can serve as a legal information assistant to support academic study, student research, and quick statutory retrieval for legal researchers. Additionally, the system provides a valuable lookup utility for internal corporate human resource (HR) compliance, enabling HR personnel to quickly identify relevant sections of the Labor Code, retirement schedules, or contract guidelines. However, despite its strong performance on the diagnostic benchmark, the system is designed to be an information lookup aid and must not be treated as a substitute for professional legal advice or qualified legal counsel. Real-world deployments should always feature explicit user-facing disclaimers and incorporate a human-in-the-loop verification step for high-stakes regulatory decisions.

\section{Limitations}
The system achieved 1.000 pass rates on the constructed benchmark, but this should be interpreted only within that benchmark and corpus. While these results reflect strong structural and citation safety, they do not prove that the system is legally perfect across all possible labor-law queries. The primary limitation of this study lies in the scope of the corpus, which contains only six indexed Vietnamese labor-law documents, and the evaluation benchmark, which consists of 69 constructed diagnostic queries. These queries were designed to test specific system capabilities rather than capture the full, messy spectrum of live user interactions, linguistic errors, and ambiguous intent. Furthermore, the system has not been subjected to full, double-blind legal expert validation, and the rule-based validation gate—while highly objective and reproducible—may miss subtle semantic errors, logical inconsistencies, or nuances in legal interpretation.

Extractive answers represent another operational trade-off, as they prioritize strict citation safety at the cost of conversational fluency and natural language adaptability. When the extractive fallback is triggered, the system returns exact statutory passages, which are highly accurate but can feel rigid compared to conversational human responses. Additionally, the system's performance remains highly dependent on upstream data engineering quality; any errors in hierarchical chunking, metadata enrichment, or cross-reference extraction will propagate down to the retrieval and answering layers. Finally, the conservative design choice to exclude 111 unresolved references outside the corpus restricts the graph query expansion policy from navigating broader legislative networks, a limitation that must be addressed before the system can scale to cover wider civil and administrative legal domains.

\begin{table}[H]
  \centering
  \caption{Limitations summary.}
  \label{tab:limitations}
  \begin{tabular}{p{0.28\linewidth}p{0.58\linewidth}}
    \toprule
    Limitation & Thesis Treatment \\
    \midrule
    Scoped corpus & Covers six indexed legal documents and does not cover all Vietnamese law. \\
    Constructed benchmark & Interpret 1.000 scores as benchmark-specific evidence only. \\
    Deterministic validation & Quality was not reviewed by human legal experts or LLM-as-Judge. \\
    Extractive answers & Extractive answers improve grounding but may be less fluent or adaptive. \\
    Upstream parsing dependence & Chunking, metadata, and reference extraction errors can affect retrieval. \\
    Legal updates & Newer or external legal sources require corpus refresh and re-evaluation. \\
    \bottomrule
  \end{tabular}
\end{table}
