\chapter{Conclusion and Future Work}

\section{Conclusion}
This thesis has investigated the integration of hybrid vector retrieval, structured document knowledge graphs, and deterministic validation checks to address the unique challenges of domain-specific legal question answering. Unlike open-domain information access, where linguistic fluency or conceptual summarization is often sufficient, legal question answering requires answers that are grounded in retrieved legal sources and supported by traceable citations. An answer lacks practical authority and compliance utility if it is not directly linked to the relevant statutory source text. Providing users with answers that preserve the specific hierarchical context of documents, articles, clauses, and points is essential to establish trust and support verifiable compliance lookups.

The research was originally motivated by a specific legal challenge: employment contract termination. Initially framed as ``A Case Study on Employment Contract Termination,'' the project aimed to assist users in navigating the complex procedures governing how labor relations end. However, during system development, it became evident that contract termination questions cannot be resolved in isolation. Dismissal disputes are deeply integrated with broader labor-law provisions, including general labor contract structures, probation rules, the fundamental rights of employees and employers, unlawful termination criteria, severance calculations, minor worker protections, retirement age tables, and civil procedure rules for court litigation. Consequently, the scope was expanded from a targeted case study to a broader scoped labor-law question-answering system covering six key Vietnamese legislative and administrative documents.

The primary technical contribution of this research is the implementation of a modular, graph-augmented Retrieval-Augmented Generation (GraphRAG) architecture. The system combines: a syntax-aware, hierarchy-aware legal chunking pipeline to parse statutory texts at leaf-level boundaries; a deterministic metadata enrichment layer to attach topics, actors, and normative ranks to each chunk; a hybrid vector-sparse retrieval index in Qdrant to match exact article coordinates and semantic synonyms concurrently; a deterministic Neo4j document-structure knowledge graph mapping explicit cross-references and normative authority; a graph-augmented retriever executing topological expansions to recover implementing regulations and tables; and a deterministic validation layer to verify that cited legal bases and article coordinates are supported by retrieved contexts.

The empirical evaluations demonstrate strong retrieval and validation performance within our controlled experimental setup. On the constructed 69-query benchmark, the proposed graph-augmented retriever achieved an average Recall@10 of 1.000, a Required Citation Coverage of 1.000, and a Forbidden Citation Violation Rate of 0.000. Furthermore, when passed through the deterministic validation checks, the integrated pipeline achieved an end-to-end pass rate of 1.000, with a 1.000 citation validation pass rate and a 1.000 answer quality pass rate, with no unsupported article numbers or unretrieved citations detected under the deterministic validation rules.

However, these results must be interpreted within their correct methodological boundaries. These performance metrics are strictly measured on the constructed 69-query benchmark and within the indexed corpus (comprising 1,556 chunks). They do not prove complete legal correctness or suggest that the system is completely free of errors under all legal scenarios. The deterministic validation checks represent a software-level verification step designed to catch structural anomalies, and they do not replace the qualified judgment of legal experts or professional legal counsel. The proposed system should therefore be understood as a legal information assistant designed to support search and compliance lookup within the indexed corpus, rather than a general legal oracle or a substitute for professional legal advice.

\section{Future Work}
Several promising developmental directions exist to expand the scope and improve the performance of this system. First, future work should expand the indexed legal corpus beyond the current six documents to include a wider range of Vietnamese labor-related laws, implementing decrees, and circulars. A key challenge in this expansion will be developing robust mechanisms to handle temporal legal updates, tracking how statutory provisions are modified, replaced, or repealed over time. Dynamic detection of amended or expired provisions will reduce the risk of retrieving obsolete legal evidence, keeping the generation context active and valid.

Second, the evaluation methodology can be refined by building an expert-validated benchmark. The current 69-query benchmark was constructed for system diagnostics, which likely underrepresents the complexity of real-world legal practice. Collaborating with Vietnamese legal professionals and labor-law scholars to curate a diverse set of gold-standard questions and answers will establish a more challenging evaluation target. Furthermore, testing the system on real, anonymized queries collected from practical scenarios will help evaluate the query router's robustness against colloquial language and ambiguous user intents.

Third, future research should focus on comparing and extending our evaluation frameworks. The deterministic, rule-based validation checks implemented in this thesis provide a reproducible and inspectable software gate to verify citation containment. However, these programmatic rules cannot evaluate semantic coherence or subtle legal interpretations. Future studies should compare this deterministic validation layer with comprehensive human legal reviews and optional, complementary LLM-as-Judge analyses. Under this approach, neural evaluation models should be treated strictly as additional diagnostic tools rather than final validation metrics.

Finally, generative answering and graph construction offer significant opportunities for refinement. The current answering pipeline prioritizes exact citation grounding and extractive evidence, which sometimes results in responses that sound repetitive. Exploring constrained abstractive generation models could help improve fluency while maintaining strict coordinate validation. Additionally, the legal knowledge graph construction can be improved by programmatically resolving external legislative references and representing structural amendments more explicitly in the database schema to support broader multi-hop statutory traversals.
